### 2024-04-05 chap_methodo/chap_methodo.tex
Intro post-review AR

The objective function of the pathway model, \ie the total transition cost $\textbf{C\textsubscript{tot,trans}}$, is computed as the sum of the total \gls{CAPEX}, \textbf{C\textsubscript{tot,capex}}, and the \gls{OPEX}, \textbf{C\textsubscript{tot,opex}} (see Eq. \ref{eq:obj_func_v2}).

@@

The total \gls{CAPEX} is the difference between the total investments done during the transition, $\textbf{C\textsubscript{inv,phase}}$, and the residual value of the assets that would still be in place after the end of the transition, $\textbf{C\textsubscript{inv,return}}$ (see Eq.  \ref{eq:CAPEX_v2}).

@@

\noindent
where $\textbf{C\textsubscript{inv,phase}}$ is given as the sum over all the  newly installed technologies at the phase $p$, $\textbf{F\textsubscript{new}}(p)$, multiplied by the average investment costs, $\emph{c\textsubscript{inv}}$,  of the year starting and ending the corresponding phase, $\emph{y\textsubscript{start}}$ and $\emph{y\textsubscript{stop}}$ respectively (see Eq. \ref{eq:PhaseInv}).

@@

\noindent where $\tau\textsubscript{\emph{phase}}$ is the annualised phase factor and $\emph{c\textsubscript{inv}}(p,j)$ is the arithmetic average of the investment cost of the technology $j$ at the beginning and the end of the phase, $\emph{c\textsubscript{inv}}(\emph{y\textsubscript{start}},j)$ and $\emph{c\textsubscript{inv}}(\emph{y\textsubscript{stop}},j)$. Similarly, the salvage value is computed in the proportion of the remaining years of life versus the initial lifetime of an installed capacity of a technology from which the anticipatively decommissioned part, $\textbf{F\textsubscript{decom}}$, is removed (see Eq. \ref{eq:salvage})

@@

About the total \gls{OPEX} of the transition, $\textbf{C\textsubscript{tot,opex}}$, on top of the initial costs in 2020, we assume that the \gls{OPEX} of a phase is equal to the average operational costs, $ \textbf{C\textsubscript{opex}}$,  of $\emph{y\textsubscript{start}}$ and $\emph{y\textsubscript{stop}}$, multiplied by the duration of a phase $\emph{t\textsubscript{phase}}$ equal to 5 years in our case (see Eq. \ref{eq:Copex_tot_v2}).

@@

\noindent
where $\textbf{C\textsubscript{opex}}(p)$ is the arithmetic average of the operational cost at the beginning and the end of the phase $p$,  $\textbf{C\textsubscript{opex}}(y\textsubscript{start})$ and $\textbf{C\textsubscript{opex}}(y\textsubscript{stop})$. The operational cost of a year, $y$, $\textbf{C\textsubscript{opex}} (y)$, is the sum of the costs related to maintenance and operation of technologies, $ \textbf{C\textsubscript{maint}}$, and the consumption of resources, $\textbf{C\textsubscript{op}}$ (see Eq. \ref{eq:opex_yearly}).

@@

he \ce{CO2}-budget for the transition, $\textbf{GWP\textsubscript{tot,trans}}$ is equal to the arithmetic average of the representative years at the beginning and the end of each phase (see Eq. \ref{eq:gwp_tot_transition}). Similarly to initial operational costs to account for the system in place in 2020 (see Eq. \ref{eq:Copex_tot_v2}), $ \textbf{GWP\textsubscript{tot}}(2020)$ accounts for the entire operational emissions in 2020, as the initial cumulative emissions of the transition. Then, as detailed in Section \ref{sec:cs:CO2-budget}, these cumulative emissions is constrained by a budget (see Eq. \ref{eq:limit_gwp_trans}).

@@

On top of these four specific sets, some artefacts were also necessary to avoid computational rounding errors. For instance, the first year of a time window is the result of the optimisation of the previous one. Therefore, optimising again this first year could lead to rounding errors preventing from the optimization to converge. For this reason,  the set $\text{YEAR}\textsubscript{ONE}$ accounts for the first representative year of the time window to optimize that is excluded from $\text{YEARS}\textsubscript{WND}$ to avoid these errors. This remark stays valid for any time window except the first one of the transition where the year 2020 is optimized even though its technological strategy is set according to the actual system presented in Appendix \ref{app:bel_2020}. Finally, as the end of time windows changes for each of them, the parameter $remaining\_years$ has to be updated accordingly to keep a meaningful definition of $\textbf{C\textsubscript{inv,return}}$ in Eq. \ref{eq:salvage}.\\

@@

The main difference lies in the myopic transition itself and especially in the earlier deployment of PVs and offshore wind turbines. These induce the reinforcement of the grid that is a capital-intensive and long-lifetime asset. This is mostly due to impact of the salvage value, Eq. \ref{eq:salvage}, in the objective function. Since this is now the transition cost over a more limited time window (\ie 10 years rather than 30 years), a bigger salvage value, deduced from the total investments, leads to a temporary better optimum at early stages of the transition. A more detailed comparison between the myopic and perfect foresight approaches is available in Appendix \ref{app:my_vs_pf}.

@@

\noindent
The PCE model ($\hat{M}$) is a representation of the relationship between the input parameters and the output variable of interest (\ie the value of the objective function, see Eq. \ref{eq:obj_func_v2}) in the EnergyScope Pathway model ($M$). This representation is constructed as a truncated series of multivariate orthonormal polynomials $\bm{\Psi}$, weighted by coefficients $u$:

@@

The process of defining the polynomial degree includes incrementally increasing it until a desired level of accuracy is achieved~\cite{coppitters2022rheia}. Starting with $p=1$, a PCE is constructed and the \gls{LOO} error is evaluated. If the \gls{LOO} error is below a specified threshold ($\sim 1\%$), the corresponding polynomial order is considered sufficient for generating an accurate PCE. However, if the error exceeds the threshold, the order is increased, and additional samples are generated following the rule of Eq.\,(\ref{eq:pce:nterms}).

For the specific study of this work, a polynomial order of 2 is necessary (with 1260 training samples as per Eq.\,(\ref{eq:pce:nterms})) to achieve a \gls{LOO} error below \SI{1}{\%} for the total transition cost.

@@

to rank parameters among each other. In (\ref{eq:mu*}), $SF_{i}$ is the distribution formed by the $r$ standardized elementary effects, as done in \citet{Moret2017PhDThesis}.

@@

Given the assumed absence of knowledge of the agent about the dynamics of the environment, \ie its transition or reward functions, we needed a so-called ``model-free'' learning algorithm. In practice, in a model-free approach, the agent estimates the optimal policy directly from experience and without estimating the dynamics of the environment. However, model-free methods suffer from two major drawbacks: their sample inefficiency and their sensitivity with respect to their hyper-parameters (\eg learning rates, exploration constants) \cite{haarnoja2018soft}. The former leads to a too expensive computational burden while the second requires meticulous settings to get good results.  To overcome these two challenges, we needed to chose between an ``on-policy'' or ``off-policy'' algorithm. In a nutshell, in on-policy learning, the agent learns the value function or policy based on the data it generates by following its current policy whereas, in off-policy, the agent can learn from data collected by any policy, not just the one it is currently following, which provides greater flexibility and potential for reusing data. This makes off-policy algorithms more data efficient and ensuring better exploration by reusing past experiences or even following random exploration \cite{haarnoja2018soft}.

@@

\gls{SAC} is a model-free and off-policy actor-critic deep \gls{RL} algorithm based on the entropy-augmented\footnote{The word ``augmented'' here is in opposition to the conventional \gls{RL} objective function that is only based on the cumulative reward, \ie first term of Eq. \ref{eq:SAC_objective}.} objective function (see Eq. \ref{eq:SAC_objective}). Where entropy represents the amount of energy in a system not available to produce work in thermodynamics, this term, also called Shannon entropy in the \gls{RL} context, stands for the randomness or stochasticity of the policy.

@@

\noindent
To characterize the variations of design within the transition under uncertainties, we have focused on the installed capacities, $\textbf{F}(y,j)$ for all $y \in \text{\emph{YEARS}}$ and $j \in \text{\emph{TECH}}$ (see Eq. \ref{eq:F_newBuilt}). Even though these represent only the design part of the result of the optimization, along with the operation, focusing on the installed capacities give a direct information regarding the required capital investment (see Eq. \ref{eq:c_inv}) and, more indirectly, the resources to use.  In other words, it captures the technological landscape of the transition.  Having defined the type of variable to consider, we need to assemble a relevant dataset. This is given by the runs to quantify the impact of the uncertain parameters on the total cost of transition required by the method described in Section \ref{sec:meth:UQ}. Overall, the original dataset is $\textbf{x}(y,j,s)$ where, on top of $y$ and $j$ previously defined, $s \in [1,2,...,S]$ stands for the sample number of the uncertainty quantification method. For the investigated case detailed in Chapter \ref{chap:atom_mol}, this represents $S=1260$ samples resulting from the perfect foresight optimization of the transition pathway under uncertainties. Finally, among the seven representative years of the transition, we do not consider 2020 as it is the initialisation year for which the design of the system is fixed, to be representative of the actual design that was in place (see Appendix \ref{app:bel_2020}). In other words, we focus here only on the years 2025, 2030, 2035, 2040, 2045 and 2050. This gives the whole dataset considered in this \gls{PCA} (see Figure \ref{fig:PCA_data}). Appendix \ref{app:UQ_tech_cap} gives the distribution of the installed capacities among the different end-use sectors from the \gls{GSA}.\\

@@

\noindent
Preprocessing the dataset before employing a method to reduce dimensionality, like \gls{PCA}, can greatly affect the structure of the simplified representation and the characteristics of the features extracted from the dataset \cite{parente2013principal,peerenboom2015dimension}. Scaling the original raw data via normalization, \ie reducing data to $[0, 1]$ interval has a double purposes: to assess variables (i) representing different sorts of features, with different units (\eg installed capacity of electricity and mobility technologies) and, (ii) ranging over the different orders of magnitude (\eg installed capacity of private and public mobility) (see Appendix \ref{app:bel_2020}).  Consequently, the first part of this data preprocessing consists in scaling the installed capacities versus their respective sector and representative year (see Eq. \ref{eq:PCA_scaling_0}). The sectors, as defined in EnergyScope, are the electricity, \gls{HT} heat, \gls{LT} heat, passenger mobility, freight mobility, \gls{NED}, storage and infrastructures. For instance, the installed capacity of \gls{PV} panels in the year $y$ of the sample $s$ is scaled by the maximum installed capacity in the electricity sector in the year $y$ among all the samples.

@@

To do so, we have arbitrarily considered these shares from the REF case, where the pathway is optimized according to the perfect foresight approach and considering all the uncertain parameters to their nominal value (see Chapter \ref{chap:atom_mol}).  The end-use-demands as well as the commodity produced for the sector coupling are based on the results of this deterministic REF case.  For instance, the share of the electricity sector accounts for its \gls{EUD} and the electricity produced to supply other sectors (\eg heat, mobility). Finally, to compare apples with apples, we converted the \gls{EUD} in the mobility sectors, \ie passenger and freight, into the \gls{FEC} they require in the REF case. This gives the second weighing factor to scale data, on top of the one of Eq. \ref{eq:PCA_scaling_0} (see Eq. \ref{eq:PCA_scaling_1}).

@@

\noindent
The final step consists in defining metrics on the whole transition based on the $\text{PC}_{y,i}$ computed for each representative year, separately. To do so, all the $\text{PC}_{y,i}$ from every year are sorted together in a descending order based on their respective variance. Then, starting with the one with the highest absolute variance, all the other $\text{PC}_{y,i}$ similar to it are clustered together. The similarity between two PCs is defined according to the cosine similarity approach, especially appropriate in high-dimensional positive spaces \cite{xia2015learning}. Indeed, as detailed in Section \ref{subsec:meth:PCA:PCA}, a PC represents a vector for which the components are related to each variable of interest. Therefore, in this work, PCs are considered similar if their cosine similarity, $S_C (A,B)$, is either greater or equal to 90\% or lower or equal to -90\% (see Eq. \ref{eq:cos_similarity}). It is important to consider to second specific case as \gls{PCA} gives the magnitude of variation within the original feature space via the components of the eigenvectors, regardless of the direction of these vectors. For instance, in a two-dimension original space, if the first PC has $(\sqrt{2}/2;\sqrt{2}/2)$ as eigenvector, this could also be $(-\sqrt{2}/2;-\sqrt{2}/2)$. The second vector being the opposite of the first, they are considered as equivalent in the regard of \gls{PCA}.

>>>>

The objective function of the pathway model, \ie the total transition cost $\textbf{C\textsubscript{tot,trans}}$, is computed as the sum of the total \gls{CAPEX}, \textbf{C\textsubscript{tot,capex}}, and the \gls{OPEX}, \textbf{C\textsubscript{tot,opex}} (see Equation (\ref{eq:obj_func_v2})).

@@

The total \gls{CAPEX} is the difference between the total investments done during the transition, $\textbf{C\textsubscript{inv,phase}}$, and the residual value of the assets that would still be in place after the end of the transition, $\textbf{C\textsubscript{inv,return}}$ (see Equation  (\ref{eq:CAPEX_v2})).

@@

\noindent
where $\textbf{C\textsubscript{inv,phase}}$ is given as the sum over all the  newly installed technologies at the phase $p$, $\textbf{F\textsubscript{new}}(p)$, multiplied by the average investment costs, $\emph{c\textsubscript{inv}}$,  of the year starting and ending the corresponding phase, $\emph{y\textsubscript{start}}$ and $\emph{y\textsubscript{stop}}$ respectively (see Equation (\ref{eq:PhaseInv})).

@@

\noindent where $\tau\textsubscript{\emph{phase}}$ is the annualised phase factor and $\emph{c\textsubscript{inv}}(p,j)$ is the arithmetic average of the investment cost of the technology $j$ at the beginning and the end of the phase, $\emph{c\textsubscript{inv}}(\emph{y\textsubscript{start}},j)$ and $\emph{c\textsubscript{inv}}(\emph{y\textsubscript{stop}},j)$. Similarly, the salvage value is computed in the proportion of the remaining years of life versus the initial lifetime of an installed capacity of a technology from which the anticipatively decommissioned part, $\textbf{F\textsubscript{decom}}$, is removed (see Equation (\ref{eq:salvage}))

@@

About the total \gls{OPEX} of the transition, $\textbf{C\textsubscript{tot,opex}}$, on top of the initial costs in 2020, we assume that the \gls{OPEX} of a phase is equal to the average operational costs, $ \textbf{C\textsubscript{opex}}$,  of $\emph{y\textsubscript{start}}$ and $\emph{y\textsubscript{stop}}$, multiplied by the duration of a phase $\emph{t\textsubscript{phase}}$ equal to 5 years in our case (see Equation (\ref{eq:Copex_tot_v2})).

@@

\noindent
where $\textbf{C\textsubscript{opex}}(p)$ is the arithmetic average of the operational cost at the beginning and the end of the phase $p$,  $\textbf{C\textsubscript{opex}}(y\textsubscript{start})$ and $\textbf{C\textsubscript{opex}}(y\textsubscript{stop})$. The operational cost of a year, $y$, $\textbf{C\textsubscript{opex}} (y)$, is the sum of the costs related to maintenance and operation of technologies, $ \textbf{C\textsubscript{maint}}$, and the consumption of resources, $\textbf{C\textsubscript{op}}$ (see Equation (\ref{eq:opex_yearly})).

@@

he \ce{CO2}-budget for the transition, $\textbf{GWP\textsubscript{tot,trans}}$ is equal to the arithmetic average of the representative years at the beginning and the end of each phase (see Equation (\ref{eq:gwp_tot_transition})). Similarly to initial operational costs to account for the system in place in 2020 (see Equation (\ref{eq:Copex_tot_v2})), $ \textbf{GWP\textsubscript{tot}}(2020)$ accounts for the entire operational emissions in 2020, as the initial cumulative emissions of the transition. Then, as detailed in Section \ref{sec:cs:CO2-budget}, these cumulative emissions is constrained by a budget (see Equation (\ref{eq:limit_gwp_trans})).

@@

On top of these four specific sets, some artefacts were also necessary to avoid computational rounding errors. For instance, the first year of a time window is the result of the optimisation of the previous one. Therefore, optimising again this first year could lead to rounding errors preventing from the optimization to converge. For this reason,  the set $\text{YEAR}\textsubscript{ONE}$ accounts for the first representative year of the time window to optimize that is excluded from $\text{YEARS}\textsubscript{WND}$ to avoid these errors. This remark stays valid for any time window except the first one of the transition where the year 2020 is optimized even though its technological strategy is set according to the actual system presented in Appendix \ref{app:bel_2020}. Finally, as the end of time windows changes for each of them, the parameter $remaining\_years$ has to be updated accordingly to keep a meaningful definition of $\textbf{C\textsubscript{inv,return}}$ in Equation (\ref{eq:salvage}).\\

@@

The main difference lies in the myopic transition itself and especially in the earlier deployment of PVs and offshore wind turbines. These induce the reinforcement of the grid that is a capital-intensive and long-lifetime asset. This is mostly due to impact of the salvage value, Equation (\ref{eq:salvage}), in the objective function. Since this is now the transition cost over a more limited time window (\ie 10 years rather than 30 years), a bigger salvage value, deduced from the total investments, leads to a temporary better optimum at early stages of the transition. A more detailed comparison between the myopic and perfect foresight approaches is available in Appendix \ref{app:my_vs_pf}.

@@

\noindent
The PCE model ($\hat{M}$) is a representation of the relationship between the input parameters and the output variable of interest (\ie the value of the objective function, see Equation (\ref{eq:obj_func_v2})) in the EnergyScope Pathway model ($M$). This representation is constructed as a truncated series of multivariate orthonormal polynomials $\bm{\Psi}$, weighted by coefficients $u$:

@@

The process of defining the polynomial degree includes incrementally increasing it until a desired level of accuracy is achieved~\cite{coppitters2022rheia}. Starting with $p=1$, a PCE is constructed and the \gls{LOO} error is evaluated. If the \gls{LOO} error is below a specified threshold ($\sim 1\%$), the corresponding polynomial order is considered sufficient for generating an accurate PCE. However, if the error exceeds the threshold, the order is increased, and additional samples are generated following the rule of Equation\,(\ref{eq:pce:nterms}).

For the specific study of this work, a polynomial order of 2 is necessary (with 1260 training samples as per Equation\,(\ref{eq:pce:nterms})) to achieve a \gls{LOO} error below \SI{1}{\%} for the total transition cost.

@@

to rank parameters among each other. In Equation (\ref{eq:mu*}), $SF_{i}$ is the distribution formed by the $r$ standardized elementary effects, as done in \citet{Moret2017PhDThesis}.

@@

Given the assumed absence of knowledge of the agent about the dynamics of the environment, \ie its transition or reward functions, we needed a so-called ``model-free'' learning algorithm. In practice, in a model-free approach, the agent estimates the optimal policy directly from experience and without estimating the dynamics of the environment. However, model-free methods suffer from two major drawbacks: their sample inefficiency and their sensitivity with respect to their hyper-parameters (\eg learning rates, exploration constants) \cite{haarnoja2018soft}. The former leads to a too expensive computational burden while the second requires meticulous settings to get good results.  To overcome these two challenges, we needed to chose between an ``on-policy'' or ``off-policy'' algorithm. In a nutshell, in on-policy learning, the agent learns the value function or policy based on the data it generates by following its current policy whereas, in off-policy, the agent can learn from data collected by any policy, not just the one it is currently following, which provides greater flexibility and potential for reusing data stored in the so-called replay buffer. This makes off-policy algorithms more data efficient and ensuring better exploration by reusing past experiences or even following random exploration \cite{haarnoja2018soft}.

@@

\gls{SAC} is a model-free and off-policy actor-critic deep \gls{RL} algorithm based on the entropy-augmented\footnote{The word ``augmented'' here is in opposition to the conventional \gls{RL} objective function that is only based on the cumulative reward, \ie first term of Equation (\ref{eq:SAC_objective}).} objective function (see Equation (\ref{eq:SAC_objective})). Where entropy represents the amount of energy in a system not available to produce work in thermodynamics, this term, also called Shannon entropy in the \gls{RL} context, stands for the randomness or stochasticity of the policy.

@@

\noindent
To characterize the variations of design within the transition under uncertainties, we have focused on the installed capacities, $\textbf{F}(y,j)$ for all $y \in \text{\emph{YEARS}}$ and $j \in \text{\emph{TECH}}$ (see Equation (\ref{eq:F_newBuilt})). Even though these represent only the design part of the result of the optimization, along with the operation, focusing on the installed capacities give a direct information regarding the required capital investment (see Equation (\ref{eq:c_inv})) and, more indirectly, the resources to use.  In other words, it captures the technological landscape of the transition.  Having defined the type of variable to consider, we need to assemble a relevant dataset. This is given by the runs to quantify the impact of the uncertain parameters on the total cost of transition required by the method described in Section \ref{sec:meth:UQ}. Overall, the original dataset is $\textbf{x}(y,j,s)$ where, on top of $y$ and $j$ previously defined, $s \in [1,2,...,S]$ stands for the sample number of the uncertainty quantification method. For the investigated case detailed in Chapter \ref{chap:atom_mol}, this represents $S=1260$ samples resulting from the perfect foresight optimization of the transition pathway under uncertainties. Finally, among the seven representative years of the transition, we do not consider 2020 as it is the initialisation year for which the design of the system is fixed, to be representative of the actual design that was in place (see Appendix \ref{app:bel_2020}). In other words, we focus here only on the years 2025, 2030, 2035, 2040, 2045 and 2050. This gives the whole dataset considered in this \gls{PCA} (see Figure \ref{fig:PCA_data}). Appendix \ref{app:UQ_tech_cap} gives the distribution of the installed capacities among the different end-use sectors from the \gls{GSA}.\\

@@

\noindent
Preprocessing the dataset before employing a method to reduce dimensionality, like \gls{PCA}, can greatly affect the structure of the simplified representation and the characteristics of the features extracted from the dataset \cite{parente2013principal,peerenboom2015dimension}. Scaling the original raw data via normalization, \ie reducing data to $[0, 1]$ interval has a double purposes: to assess variables (i) representing different sorts of features, with different units (\eg installed capacity of electricity and mobility technologies) and, (ii) ranging over the different orders of magnitude (\eg installed capacity of private and public mobility) (see Appendix \ref{app:bel_2020}).  Consequently, the first part of this data preprocessing consists in scaling the installed capacities versus their respective sector and representative year (see Equation (\ref{eq:PCA_scaling_0})). The sectors, as defined in EnergyScope, are the electricity, \gls{HT} heat, \gls{LT} heat, passenger mobility, freight mobility, \gls{NED}, storage and infrastructures. For instance, the installed capacity of \gls{PV} panels in the year $y$ of the sample $s$ is scaled by the maximum installed capacity in the electricity sector in the year $y$ among all the samples.

@@

To do so, we have arbitrarily considered these shares from the REF case, where the pathway is optimized according to the perfect foresight approach and considering all the uncertain parameters to their nominal value (see Chapter \ref{chap:atom_mol}).  The end-use-demands as well as the commodity produced for the sector coupling are based on the results of this deterministic REF case.  For instance, the share of the electricity sector accounts for its \gls{EUD} and the electricity produced to supply other sectors (\eg heat, mobility). Finally, to compare apples with apples, we converted the \gls{EUD} in the mobility sectors, \ie passenger and freight, into the \gls{FEC} they require in the REF case. This gives the second weighing factor to scale data, on top of the one of Equation (\ref{eq:PCA_scaling_0}) (see Equation (\ref{eq:PCA_scaling_1})).

@@

\noindent
The final step consists in defining metrics on the whole transition based on the $\text{PC}_{y,i}$ computed for each representative year, separately. To do so, all the $\text{PC}_{y,i}$ from every year are sorted together in a descending order based on their respective variance. Then, starting with the one with the highest absolute variance, all the other $\text{PC}_{y,i}$ similar to it are clustered together. The similarity between two PCs is defined according to the cosine similarity approach, especially appropriate in high-dimensional positive spaces \cite{xia2015learning}. Indeed, as detailed in Section \ref{subsec:meth:PCA:PCA}, a PC represents a vector for which the components are related to each variable of interest. Therefore, in this work, PCs are considered similar if their cosine similarity, $S_C (A,B)$, is either greater or equal to 90\% or lower or equal to -90\% (see Equation (\ref{eq:cos_similarity})). It is important to consider to second specific case as \gls{PCA} gives the magnitude of variation within the original feature space via the components of the eigenvectors, regardless of the direction of these vectors. For instance, in a two-dimension original space, if the first PC has $(\sqrt{2}/2;\sqrt{2}/2)$ as eigenvector, this could also be $(-\sqrt{2}/2;-\sqrt{2}/2)$. The second vector being the opposite of the first, they are considered as equivalent in the regard of \gls{PCA}.

### 2024-04-05 options/symbols_and_cmd.tex
RobPol - Description case ROB
Intro post-review AR

% ---------------------------------------------------------------------------- %
% ACRONYMS
%% A
\newabbreviation[group={Acronyms}]{API}{API}{application programming interface}

%% B
\newabbreviation[group={Acronyms}]{BECCS}{BECCS}{bioenergy with carbon capture and storage}
\newabbreviation[group={Acronyms}]{BEV}{BEV}{battery electric vehicle}
\newabbreviation[group={Acronyms}]{BTX}{BTX}{benzene, toluene and xylene}

%% C
\newabbreviation[group={Acronyms}]{CAPEX}{CAPEX}{capital expenditure}
\newabbreviation[group={Acronyms}]{CCGT}{CCGT}{combined cycle gas turbine}
\newabbreviation[group={Acronyms}]{CCS}{CCS}{carbon capture and storage}
\newabbreviation[group={Acronyms}]{CHP}{CHP}{combined heat and power}
\newabbreviation[group={Acronyms}]{CNG}{CNG}{compressed natural gas}

%% D
\newabbreviation[group={Acronyms}]{DHN}{DHN}{district heating network}

%% E
\newabbreviation[group={Acronyms}]{ESOMs}{ESOMs}{energy system optimisation models}
\newabbreviation[group={Acronyms}]{ESTD}{EnergyScope TD}{EnergyScope Typical Days}
\newabbreviation[group={Acronyms}]{EUD}{EUD}{end-use demand}

%% F
\newabbreviation[group={Acronyms}]{FC}{FC}{fuel cell}

%% G
\newabbreviation[group={Acronyms}]{GDP}{GDP}{gross domestic product}
\newabbreviation[group={Acronyms}]{GHG}{GHG}{greenhouse gases}
\newabbreviation[group={Acronyms}]{GSA}{GSA}{global sensitivity analysis}
\newabbreviation[group={Acronyms}]{GWP}{GWP}{global warming potential}

%% H
\newabbreviation[group={Acronyms}]{HP}{HP}{heat pump}
\newabbreviation[group={Acronyms}]{HT}{HT}{high-temperature}
\newabbreviation[group={Acronyms}]{HVC}{HVC}{high value chemicals}

%% I
\newabbreviation[group={Acronyms}]{ICE}{ICE}{internal combustion engine}
\newabbreviation[group={Acronyms}]{IEA}{IEA}{International Energy Agency}
\newabbreviation[group={Acronyms}]{IPCC}{IPCC}{intergovernmental panel for climate change}
\newabbreviation[group={Acronyms}]{IQR}{IQR}{interquatile range}

%% L
\newabbreviation[group={Acronyms}]{LCA}{LCA}{life cycle assessment}
\newabbreviation[group={Acronyms}]{LCOE}{LCOE}{levelised cost of energy}
\newabbreviation[group={Acronyms}]{LFO}{LFO}{light fuel oil}
\newabbreviation[group={Acronyms}]{LOO}{LOO}{leave-one-out}
\newabbreviation[group={Acronyms}]{LPG}{LPG}{liquefied petroleum gas}
\newabbreviation[group={Acronyms}]{LT}{LT}{low-temperature}

%% M
\newabbreviation[group={Acronyms}]{MDP}{MDP}{Markov decision process}
\newabbreviation[group={Acronyms}]{MMSA}{MMSA}{Methanol Market Services Asia}
\newabbreviation[group={Acronyms}]{MTBE}{MTBE}{methyl tert-butyl ether}
\newabbreviation[group={Acronyms}]{MTO}{MTO}{methanol-to-olefins}

%% N
\newabbreviation[group={Acronyms}]{NED}{NED}{non-energy demand}
\newabbreviation[group={Acronyms}]{NG}{NG}{fossil gas}
\newabbreviation[group={Acronyms}]{NN}{NN}{neural network}
\newabbreviation[group={Acronyms}]{NRE}{NRE}{non-renewable energy}
\newabbreviation[group={Acronyms}]{NSC}{NSC}{naphtha steam cracker}

%% O
\newabbreviation[group={Acronyms}]{OPEX}{OPEX}{operational expenditure}

%% P
\newabbreviation[group={Acronyms}]{PC}{PC}{principal component}
\newabbreviation[group={Acronyms}]{PCA}{PCA}{Principal Component Analysis}
\newabbreviation[group={Acronyms}]{PCE}{PCE}{Polynomial Chaos Expansion}
\newabbreviation[group={Acronyms}]{PDF}{PDF}{probability density function}
\newabbreviation[group={Acronyms}]{PV}{PV}{photovoltaic}

%% R
\newabbreviation[group={Acronyms}]{RE}{RE}{renewable energy}
\newabbreviation[group={Acronyms}]{RL}{RL}{reinforcement learning}

%% S
\newabbreviation[group={Acronyms}]{SAC}{SAC}{Soft Actor Critic}
\newabbreviation[group={Acronyms}]{SDGs}{SDGs}{Sustainable Development Goals}
\newabbreviation[group={Acronyms}]{SMR}{SMR}{small modular reactor}
\newabbreviation[group={Acronyms}]{SVD}{SVD}{singular value decomposition}

@@

%% V
\newabbreviation[group={Acronyms}]{VRES}{VRES}{variable renewable energy sources}

>>>>

% ---------------------------------------------------------------------------- %
% ACRONYMS
%% A
\newabbreviation[group={Acronyms}]{API}{API}{Application Programming Interface}

%% B
\newabbreviation[group={Acronyms}]{BECCS}{BECCS}{Bioenergy with Carbon Capture and Storage}
\newabbreviation[group={Acronyms}]{BEMS}{BEMS}{Building Energy Management System}
\newabbreviation[group={Acronyms}]{BEV}{BEV}{Battery Electric Vehicle}
\newabbreviation[group={Acronyms}]{BTX}{BTX}{Benzene, Toluene and Xylene}

%% C
\newabbreviation[group={Acronyms}]{CAPEX}{CAPEX}{Capital Expenditure}
\newabbreviation[group={Acronyms}]{CCGT}{CCGT}{Combined Cycle Gas Turbine}
\newabbreviation[group={Acronyms}]{CCS}{CCS}{Carbon Capture and Storage}
\newabbreviation[group={Acronyms}]{CHP}{CHP}{Combined Heat and Power}
\newabbreviation[group={Acronyms}]{CNG}{CNG}{Compressed Natural Gas}

%% D
\newabbreviation[group={Acronyms}]{DC}{DC}{Direct Current}
\newabbreviation[group={Acronyms}]{DHN}{DHN}{District Heating Network}
\newabbreviation[group={Acronyms}]{DNN}{DNN}{Deep Neural Network}
\newabbreviation[group={Acronyms}]{DRL}{DRL}{Deep Reinforcement Learning}

%% E
\newabbreviation[group={Acronyms}]{ESOMs}{ESOMs}{Energy System Optimisation Models}
\newabbreviation[group={Acronyms}]{EUD}{EUD}{End-Use Demand}

%% F
\newabbreviation[group={Acronyms}]{FC}{FC}{Fuel Cell}
\newabbreviation[group={Acronyms}]{FEC}{FEC}{Final Energy Consumed}

%% G
\newabbreviation[group={Acronyms}]{GDP}{GDP}{Gross Domestic Product}
\newabbreviation[group={Acronyms}]{GHG}{GHG}{Greenhouse Gases}
\newabbreviation[group={Acronyms}]{GSA}{GSA}{Global Sensitivity Analysis}
\newabbreviation[group={Acronyms}]{GWP}{GWP}{Global Warming Potential}

%% H
\newabbreviation[group={Acronyms}]{HP}{HP}{Heat Pump}
\newabbreviation[group={Acronyms}]{HT}{HT}{High-Temperature}
\newabbreviation[group={Acronyms}]{HVC}{HVC}{High-Value Chemicals}

%% I
\newabbreviation[group={Acronyms}]{IAMs}{IAMs}{Integrated Assessment Models}
\newabbreviation[group={Acronyms}]{ICE}{ICE}{Internal Combustion Engine}
\newabbreviation[group={Acronyms}]{IEA}{IEA}{International Energy Agency}
\newabbreviation[group={Acronyms}]{IPCC}{IPCC}{Intergovernmental Panel on Climate Change}
\newabbreviation[group={Acronyms}]{IQR}{IQR}{Interquatile Range}

%% L
\newabbreviation[group={Acronyms}]{LCA}{LCA}{Life Cycle Assessment}
\newabbreviation[group={Acronyms}]{LCOE}{LCOE}{Levelised Cost of Energy}
\newabbreviation[group={Acronyms}]{LFO}{LFO}{Light Fuel Oil}
\newabbreviation[group={Acronyms}]{LOO}{LOO}{Leave-One-Out}
\newabbreviation[group={Acronyms}]{LP}{LP}{Linear Programming}
\newabbreviation[group={Acronyms}]{LPG}{LPG}{Liquefied Petroleum Gas}
\newabbreviation[group={Acronyms}]{LT}{LT}{Low-Temperature}

%% M
\newabbreviation[group={Acronyms}]{MDP}{MDP}{Markov Decision Process}
\newabbreviation[group={Acronyms}]{MMSA}{MMSA}{Methanol Market Services Asia}
\newabbreviation[group={Acronyms}]{MTBE}{MTBE}{Methyl Tert-butyl Ether}
\newabbreviation[group={Acronyms}]{MTO}{MTO}{Methanol-to-olefins}

%% N
\newabbreviation[group={Acronyms}]{NED}{NED}{Non-energy Demand}
\newabbreviation[group={Acronyms}]{NG}{NG}{Fossil Gas}
\newabbreviation[group={Acronyms}]{NN}{NN}{Neural Network}
\newabbreviation[group={Acronyms}]{NRE}{NRE}{Non-renewable Energy}
\newabbreviation[group={Acronyms}]{NSC}{NSC}{Naphtha Steam Cracker}

%% O
\newabbreviation[group={Acronyms}]{OPEX}{OPEX}{Operational Expenditure}

%% P
\newabbreviation[group={Acronyms}]{PC}{PC}{Principal Component}
\newabbreviation[group={Acronyms}]{PCs}{PCs}{Principal Components}
\newabbreviation[group={Acronyms}]{PCA}{PCA}{Principal Component Analysis}
\newabbreviation[group={Acronyms}]{PCE}{PCE}{Polynomial Chaos Expansion}
\newabbreviation[group={Acronyms}]{PDF}{PDF}{Probability Density Function}
\newabbreviation[group={Acronyms}]{PV}{PV}{Photovoltaic}

%% R
\newabbreviation[group={Acronyms}]{RE}{RE}{Renewable Energy}
\newabbreviation[group={Acronyms}]{RL}{RL}{Reinforcement Learning}

%% S
\newabbreviation[group={Acronyms}]{SAC}{SAC}{Soft Actor Critic}
\newabbreviation[group={Acronyms}]{SMR}{SMR}{Small Modular Reactor}
\newabbreviation[group={Acronyms}]{SVD}{SVD}{Singular Value Decomposition}

%% S
\newabbreviation[group={Acronyms}]{TRL}{TRL}{Technology Readiness Level}

@@

%% V
\newabbreviation[group={Acronyms}]{VRES}{VRES}{Variable Renewable Energy Sources}
